Light and growth form interact to shape stomatal ratio among British angiosperms

### 2017-11-15 ms/ms.Rnw
added citation to ms
small change to ms

Natural selection shapes leaf anatomy in order to optimize its photosynthetic function in a given environment \citep{Haberlandt_1914, Givnish_1987, Smith_etal_1997}. By understanding the adaptive significance of leaf anatomical variation we can learn about natural history, find targets for crop improvement, and identify anatomical proxies for paleoclimates preserved in the fossil record \citep[e.g.][]{Wolfe_1971, Royer_2001, McElwain_Steinthorsdottir_2017}. The size, density, and distribution of stomata on a leaf vary widely and impact the flux of CO$_2$ and water vapour \citep[recently reviewed in][]{Sack_Buckley_2016}, as well as susceptibility to foliar pathogens that infect through stomata \citep{Mckown_etal_2014, Melotto_etal_2017}. Hence, stomata have been especially useful in understanding plastic and evolutionary response to climate change and domestication \citep{Woodward_1987, Beerling_Royer_2011, Milla_etal_2013}.

>>>>

Natural selection shapes leaf anatomy in order to optimize its photosynthetic function in a given environment \citep{Haberlandt_1914, Givnish_1987, Smith_etal_1997}. By understanding the adaptive significance of leaf anatomical variation we can learn about natural history, find targets for crop improvement, and identify anatomical proxies for paleoclimates preserved in the fossil record \citep[e.g.][]{Wolfe_1971, Royer_2001, McElwain_Steinthorsdottir_2017}. The size, density, and distribution of stomata on a leaf vary widely and impact the flux of CO$_2$ and water vapour \citep[recently reviewed in][]{Sack_Buckley_2016}, as well as susceptibility to foliar pathogens that infect through stomata \citep{Mckown_etal_2014, Melotto_etal_2017}. Hence, stomata have been especially useful in understanding plastic and evolutionary responses to climate change and domestication \citep{Woodward_1987, Beerling_Royer_2011, Milla_etal_2013}.
